Temporary Landing Page for Longitudinal Project

### 2023-04-29 index.qmd
updated LDA Struct image for manuscript 2

---
#title: "Longitudinal Analysis"
format:
  html:
    page-layout: full
    grid:
      sidebar-width: 0px
      body-width: 2000px
      margin-width: 0px
      gutter-width: 1.5rem
---

![](./figures/Figlanding4.svg)

>>>>

---
#title: "Longitudinal Analysis"
format:
  html:
    css: styles.css
    theme: cosmo
    page-layout: full
    grid:
      sidebar-width: 250px
      body-width: 2000px
      margin-width: 100px
    gutter-width: 1.5rem
---

::: {.grid}

::: {.g-col-12}
![](./figures/Figlanding5.svg)
:::

:::
